\begin{DndMonster}{Agna Fire Smith}
    \begin{multicols}{2}
        \DndMonsterType{Medium humanoid (half-orc), lawful neutral}

        \DndMonsterBasics[
            armor-class = {16 (chain mail)},
            hit-points  = {\DndDice{16d8 + 32}},
            speed       = {30 ft.},
        ]

        \DndMonsterAbilityScores[
            str = 19,
            dex = 13,
            con = 16,
            int = 11,
            wis = 14,
            cha = 16,
        ]

        \DndMonsterDetails[
            saving-throws = {Str +8, Con +7, Cha +7},
            skills = {Athletics +12, Intimidation +7, Religion +4, Survival +6},
            damage-resistances = {bludgeoning, poison},
            senses = {darkvision 60 ft., passive Perception 12},
            languages = {Common, Orc},
            challenge = 9
        ]

        \DndMonsterAction{Brute}
        A melee weapon deals one extra die of its damage when Agna hits with it (included in the attack).

        \DndMonsterAction{Pushback}
        Whenever Agna hits a creature with an unarmed strike, the target is pushed back 5 feet.
        If the creature can not move back because it is blocked by a solid object like a wall, it takes an additional \DndDice{1d4} bludgeoning damage.
        The target must succeed on a DC 17 Strength saving throw or be knocked prone.

        \DndMonsterAction{Relentless Endurance (1/day)}
        When Agna is reduced to 0 hit points but not killed outright, she can drop to 1 hit point instead.
        She can’t use this feature again until the next dawn.

        \DndMonsterSection{Actions}

        \DndMonsterAction{Multiattack}
        Agna makes two attacks in one action. She can use any of her attacks twice.

        \DndMonsterMelee[
            name=Maul +2,
            mod=+10,
            dmg=\DndDice{2d6 + 6},
            dmg-type=bludgeoning,
        ]
        A maul, Agna worked on for many years in order to perfect its weight and balance.

        \DndMonsterMelee[
            name=Warhammer,
            mod=+8,
            dmg=\DndDice{1d8 + 4},
            dmg-type=bludgeoning,
            or-dmg={1d10 + 4},
            or-dmg-when={if used with two hands.}
        ]

        \DndMonsterMelee[
            name=Unarmed Strike,
            mod=+8,
            dmg=5,
            dmg-type=bludgeoning
        ]

        \DndMonsterSection{Reactions}

        \DndMonsterAction{Parry}
        Agna adds 2 to her AC against one melee attack that would hit her.
        To do so, she must see the attacker and be wielding a melee weapon.

        \DndMonsterSection{Inventory}

        \DndMonsterAction{Chain Mail}
        A set of chain mail armor, crafted by Agna herself.
        She often wears it to protect herself when working with especially dangerous tools.

        \DndMonsterAction{Common Clothes}
        Heavy leather clothes with burn and cut marks all over them.
        She spends a lot of time to take care of it, applying oils and repairing tears.

        \DndMonsterAction{Gaming Set of Playing Cards}
        A set of Orcish playing cards.
        Agna often visits Brookton's taverns, enjoying a good and fair game of cards along with the occasional ale or two.

        \DndMonsterAction{Smith's Tools}
        The tools of her trade.
        She carries them around almost all the time, using them to repair what ever is broken while enjoying her time off in the town.

        \DndMonsterAction{Pan Flute}
        Agna uses this set of panpipes during her meditation rituals.
        Due to her having picked them up only recently, the sounds she produces from them are not as pleasing as one might hope.

    \end{multicols}
\end{DndMonster}