\begin{DndMonster}{Bridget Reede}
    \begin{multicols}{2}
        \DndMonsterType{Medium humanoid (human), chaotic good}

        \DndMonsterBasics[
            armor-class = {10},
            hit-points  = {\DndDice{6d8 + 2}},
            speed       = {30 ft.},
        ]

        \DndMonsterAbilityScores[
            str = 11,
            dex = 11,
            con = 15,
            int = 15,
            wis = 9,
            cha = 15,
        ]

        \DndMonsterDetails[
            saving-throws = {Con +4, Cha +4},
            skills = {History +4, Insight +1, Nature +4, Persuasion +4},
            senses = {passive Perception 9},
            languages = {Common, Dwarvish, Hafling},
            challenge = 1
        ]

        \DndMonsterAction{Spellcasting}
        Bridget is a 1st-level spellcaster.
        Her spellcasting ability is Charisma (spell save DC 12, +4 to hit with spell attacks).
        Bridget has the following spells prepared:
        \begin{DndMonsterSpells}
            \DndMonsterSpellLevel{druidcraft, prestidigitation, thaumaturgy}
        \end{DndMonsterSpells}

        \DndMonsterAction{Steadfast}
        Bridget can't be frightened while she can see an allied creature withing 30 feet of her.

        \DndMonsterSection{Actions}

        \DndMonsterAttack[
            name=Dagger,
            distance=both,
            mod=+2,
            range=20/60,
            dmg=\DndDice{1d4},
            dmg-type=piercing,
        ]

        \DndMonsterRanged[
            name=Sling,
            mod=+2,
            range=30/120,
            dmg=\DndDice{1d4},
            dmg-type=bludgeoning
        ]

        \DndMonsterMelee[
            name=Unarmed Strike,
            mod=+2,
            dmg=1,
            dmg-type=bludgeoning
        ]

        \DndMonsterAction{Healer's Kit}
        This kit is a leather pouch containing bandages, salves, and splints.
        The kit has ten uses.
        As an action, Bridget can expend one use of the kit to stabilize a creature that has 0 hit points, without needing to make a Wisdom (Medicine) check.

        \DndMonsterAction{Potion of Healing}
        The potion's red liquid glimmers when agitated.
        As a bonus action, Bridget can either consume the potion herself, or administer it to a creature within 5 feet of her.
        The consuming creature regains \DndDice{2d4 + 2} hit points.

        \DndMonsterSection{Inventory}

        \DndMonsterAction{Brewer's Supplies}
        These special tools include the items needed to pursue a craft or trade in brewing.

        \DndMonsterAction{Cloak of Protection}
        \textit{Wondrous item, (attuned)}
        Bridget gains a +1 bonus to her AC and saving throws when wearing this cloak.

        \DndMonsterAction{Common Clothes}
        A slightly off-white, puffy blouse over which Bridget wears a forest green west made from a thick cotton weave.
        A forest green skirt reaching almost to the ground under which a pair of cloth boots with leather soles can be seen.

        \DndMonsterAction{Cook's Utensils}
        These special tools include the items needed to pursue a craft or trade in cookery.

        \DndMonsterAction{Disguise Kit}
        This pouch of cosmetics, hair dye, and small props lets Bridget create disguises that change a creature's physical appearance.

        \DndMonsterAction{Gaming Set of Playing Cards}
        A set of cards Bridget uses to play Three Dragon Ante with guests and friends.

        \DndMonsterAction{Herbalism Kit}
        This kit contains a variety of instruments such as clippers, mortar and pestle, and pouches and vials used by herbalists to create remedies and potions.

        \DndMonsterAction{Glass Bottle}
        A bottle holding 1½ pints of liquid.

        \DndMonsterAction{Pouch}
        A small leather pouch in which Bridget keeps her sling bullets and assorted bips and bops she finds on her way through the woods.

        \DndMonsterAction{Ring of Protection}
        \textit{Ring, rare (attuned)}
        Bridget gains a +1 bonus to her AC and saving throws when wearing this ring.

        \DndMonsterAction{Sling Bullet (20)}
        A small stone which can be flung at high velocity using Bridget's sling.

        \DndMonsterAction{Tinderbox}
        This small container holds flint, fire steel, and tinder (usually dry cloth soaked in light oil) used to kindle a fire.

    \end{multicols}
\end{DndMonster}