\chapter{Faces of Glaefall}

This chapter describes the friendly, or not so friendly, characters the players might encouter throughout their adventure.

\begin{multicols}{2}

\section{Agna Fire Smith}

Agna Fire Smith (half-orc, she/her) is the blacksmith of Brookton.
Her workshop is located at the outskirts of town to not annoy the whole town while she is working.
She spends most of her time working in that exact workshop, producing everything from door hinges to swords and shields.
However, Agna makes a point of taking enough time to also work on her inner peace.
In recent years, she has taken up the practice of searching a quiet place in the forest to meditate.

\begin{DndSidebar}{Interest and Forces}
    Although skeptical at first, Agna has become in integral part of Brookton.
    She provides the town with many needed tools, mechanical parts, etc.
    
    Agna has the following main interests:
    \begin{itemize}
        \item{Find someone to teach her how to imbue her products with magic}
        \item{Keep the town independent and safe}
        \item{Get a better contract with the dwarves in Stonefell}
    \end{itemize}
    
    Agna is subject to the following forces:
    \begin{itemize}
        \item{I want to learn to produce jewelry --- \textbf{BUT} --- I have no one to teach me.}
        \item{I want to have my own metal mine --- \textbf{BUT} --- There are no resources near the town.}
        \item{I want a better contract with the dwarves --- \textbf{BUT} --- They are hesitant because I am of orcish descent.}
    \end{itemize}
\end{DndSidebar}

Agna is usually dressed in heavy leather clothing, she uses to protect herself from accidental spillage of molten metal or burning herself on freshly forged items.
On her hip, she carries a tool belt equipped with every hand tool a blacksmith's heart desires.
Most of those tools the fabricated herself, and she likes to show them off as a way to express the pride she has into her craft.
Her feet are protected by heavy leather boots, whose tips are covered in steel.
While Agna prefers to keep her long ebony hair open when she is on her way through town, she makes sure to bind it up tightly when at her workshop.
Despite her effort to protect herself from the hazards of her craft, her arms and hands a littered with small burn scars.

When she first arrived in town, many were a little skeptical whether she would fit in.
Almost no one had seen a fully fleshed orc around the woods of Glaefall.
The townsfolk decided to be open and welcoming toward Agna and after a few weeks many of them would have sworn she had been living in Brookton since the dawn  of time.

\section{Bridget Reede}

Bridget (human, she/her) is the proprietor of the Brookton Inn, located about 30 minutes down the road from Brookton proper.
She is in her early thirties and took over the inn from her parents when they moved to Stillwharf.
Most of her time is spent cooking all sorts of hearty meals and baking bread that allegedly is to die for.
When she is not preparing food for her guests, she enjoys chatting and gossiping with her patrons.
She is known for playing a mean hand of Three Dragon Ante, so much so that people who don't know her might suspect her of cheating.

\begin{DndSidebar}{Interest and Forces}
    What the townsfolk love most about Bridget is her loving and welcoming nature.
    It is because of these qualities or hers, that despite being located outside of town, the Brookton Inn is very much an integral social component of every Brooktonian's life.

    Bridget has the following main interests:
    \begin{itemize}
        \item{Get to know interesting people from all around the world}
        \item{Provide a safe environment for everyone}
        \item{Qualify for a Magic License}
    \end{itemize}

    Bridget is subject to the following forces:
    \begin{itemize}
        \item{I want to spend more time with Conny --- \textbf{BUT} --- I need to keep the inn open.}
        \item{I want to get a formal training in magic --- \textbf{BUT} --- I cannot afford the cost.}
        \item{I want for Conny and Zingora to be a family again --- \textbf{BUT} --- The rift between them has grown over many decades.}
    \end{itemize}
\end{DndSidebar}

She usually wears simple clothes, namely a slightly off-white and puffy blouse.
Over her blouse, she usually wears one of her cotton vests.
Her legs are covered by a matching skirt that almost reaches to the ground.
From underneath her skirt, simple dark gray cloth boots with thick leather soles peak out.
Due to sanitary reasons, she wears her burgundy hair made up into a simple bun when she is at work in the inn.
During her off-time however, she enjoys wearing her hair open, reaching a couple of inches below her shoulders.

On the tenth day of the week she can often be found taking a walk in the forest, picking mushrooms or pillow moss.
She also likes to visit the Merfolk near Glimmercove to trade news and gossip in exchange for their delicious Merfoam Bubbles.
From time to time however, one would be able to meet her at the hidden hut of Conny, the ``Hemlock Witch'', assuming one knows how to find it.
Bridget is convinced that not a single Brooktonian knows about her and Conny, but then she also believes her super secret Foamcake recipe is actually a secret.

With only little time to pursue activities outside the inn, Bridget has dabbled in learning basic spells to help around the house and amuse the guests.
For the longest time she tried to convince Leofric to teach her how to apply her magic more effectively, but he insisted that ``Magic is best learned on your own, Bridgi!''
Since the new laws have gone into effect however, she was too worried about getting caught without a license to continue practicing.

\section{Clop}

Clop (treant, they/them) are one of the oldest inhabitants of the forests of Glaefall.
They have been living in the forest ever since they were just a tiny seedling.
Over 500 years have passed since that time, although Clop have not kept track after about 200 years.
They spend most of their time wandering slowly through the forest, which is tough given how dense the forest is and how tall they are.

Despite all their wandering, they tend to stay near one of the many paths that lead through the forest.
Clop's primary motivation to do so is their curiosity about what they call ``The Tiny People''.
They like to inspect everything from gnomes to large goliaths if they happen to see them on the trail.
In all of these encounters, Clop make it a point to be gentle when picking up one of ``The Tiny People'', in order not to hurt them.

Clop enjoy a good conversation, and they are always interested in what is happening outside the forest.
One of their closest friend is Bridget.
Both of them make it a point to meet at least once a month to discuss the happening in- and outside the forest, and to exchange gossip.

The easiest way, at least for an eagle-eyed observer, to spot Clop is to take note of their name tag.
When Bridget first met Clop, she decided to knit them a name tag, to make it easier for her to find them.
Clop's name tag is made from a glittering, color changing wool, Bridget obtained in a trade with Leofric.

\end{multicols}
