\subsection{Mermaids}

Similar to more common Merfolk, mermaids are aquatic humanoids with the lower body of a fish.

\subsubsection{Relation to Merfolk}
Because of their similarities, new arrivals to Glaefall often confuse them with ordinary Merfolk.
However, the mermaids of Glaefall are not related to Merfolk in any way.

\subsubsection{Appearance}
Their slightly translucent skin, showing the deep blue blood flowing in their veins, is usually colored somewhere between turquoise and light blue.
Their webbed fingers and large fish tails make grant them excellent speed and dexterity in water.
Contrary to Merfolk however, mermaids can only breathe for a short time on land and must return to water rather quickly.

\subsubsection{Living Space}
Stemming from a place between the Feywild and the Celestial Plane, mermaids have settled in the Glimmerbay.
They tend to crystals growing withing the caves of the bay, defending them from anyone trying to steal them.
Known for growing the famed Bubbleweed, a priced ingredient in potions as well as dishes generally only enjoyed by nobility, the mermaid's diet is primarily plant based.

\subsubsection{Behavior}
The Glaefall mermaids live as a single cohesive tribe.
Abiding by a strong moral code, mermaids generally do not get involved in the matters of others, but protect their kind and settlement fiercely against thieves and intruders.
Even though they are innately curious about the world around them, they generally do not show themselves to people visiting the bay for the first time.

\begin{DndMonster}[float, floatplacement=!htb]{Mermaid}
    \DndMonsterType{Medium fey, lawful neutral}

    \DndMonsterBasics[
        armor-class = {15},
        hit-points  = {\DndDice{11d12 + 6}},
        speed       = {5 ft., swim 40 ft.},
    ]

    \DndMonsterAbilityScores[
        str = 10,
        dex = 16,
        con = 14,
        int = 10,
        wis = 18,
        cha = 12,
    ]

    \DndMonsterDetails[
        skills = {Arcana +6, Athletics +6, Insight +4, Stealth +4},
        damage-vulnerabilities = {fire},
        damage-resistances = {cold, poison},
        senses = {darkvision 90 ft., passive Perception 12},
        languages = {Speaks Sylvan. Can understand Common and Sylvan. Telepathy 120 ft.},
        challenge = 3,
    ]

    \DndMonsterAction{Innate Spellcasting}
    A mermaid's spellcasting ability is Wisdom (spell save DC 14, +4 to hit with spell attacks).
    A mermaid can innately cast the following spells, requiring no material components:
    \begin{DndMonsterSpells}
        \DndInnateSpellLevel{druidcraft, minor illusion, charm person, cure wounds}
        \DndInnateSpellLevel[1]{dominate beast, dominate person}
    \end{DndMonsterSpells}

    \DndMonsterAction{Natural Camouflage}
    Mermaids naturally adapt to their surroundings and can hide between plants and rock formations.
    Creatures looking for a mermaid must succeed on a Wisdom (Perception) DC 15 check.
    If a mermaid is hidden when entering initiative, all creatures must beat a passive Wisdom (Perception) DC 15 check or be surprised.

    \DndMonsterAction{Theater of the Mind}
    Due to their extra-planar origin, mermaids possess strong powers of illusion, which they use to hide from perceived enemies.
    A mermaid may employ this power on a creature to show the target its darkest nightmares.
    This ability may only be used if the mermaid is hidden from the targeted creature.
    A targeted creature must succeed on a Wisdom saving throw DC 15 or take \DndDice{2d6 + 4} psychic damage.

    \DndMonsterSection{Actions}
    \DndMonsterAction{Multiattack}
    The mermaid makes two Claw attacks.

    \DndMonsterMelee[
        name     = {Claw},
        mod      = {+5},
        dmg      = {\DndDice{2d8}},
        dmg-type = {slashing}
    ]

    \DndMonsterMelee[
        name     = {Solar Finger Snap},
        mod      = {+5},
        dmg      = {\DndDice{3d6 + 3}},
        dmg-type = {radiant},
        extra    = {, and the target must make a DC 13 Constitution saving throw. On a failed save, the target is blinded until the start of the mermaid's next turn}
    ]

    \DndMonsterMelee[
        name     = {Tail Whip},
        mod      = {+5},
        dmg      = {\DndDice{2d10 + 3}},
        dmg-type = {bludgeoning},
        extra    = {, and the target must make a DC 15 Dexterity saving throw. On a failed save, the target is pushed 20 ft. away from the mermaid without provoking any reactions}
    ]
\end{DndMonster}